Instructions for TTO 2019 Proceedings

### 2021-07-05 article/test.tex
upadate

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. {\color{red} Fact-checkers + no laws or not so much.}

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data. We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

\begin{figure}
	\centering
	\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

{\color{red} N.B. Manual decision, not the automatic strike system}
\begin{figure}
\centering
\includegraphics[scale=0.35]{./img/lifesite.jpg} 
\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }

@@

\href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}

We gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a not-for-profit organization verifying the credibility of influential claims and media coverage that claims to be scientific. As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets were marked with the notice { ``Get the facts about COVID-19''}, $5$ tweets were marked with { ``Learn about US 2020 election security efforts''} and only $1$ tweet was marked with the notice {``This claim about election fraud is disputed''}. Furthermore, we noticed that there exists tweets that share the exact same URL links marked as False, yet only a few get marked by a notice.

Furthermore,

@@

{ \color{pink} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria. We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore. This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.

To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent. But too much transparency on how the regulation policies are exactly implemented can actually backfire. For example YouTube is certainly applying an 'information' banner on all videos mentioning Covid and related terms in their title. Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'. If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation. There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.

There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms. For example Newsguard, blablabla... In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2

Recommendation: inform about sources, example inform users that this user shared x failed fact-checks. }
%→ Littérature liée aux effets psychologiques 
%→ multi-platforming, indirect effects, etc. 
%→ strategies

\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
\newpage

@@

%Guillaume Plique, Pauline Breteau, Jules Farjas, Héloïse Théro, & Jean Descamps. (2019, October 14). Minet, a webmining CLI tool & library for python. Zenodo. http://doi.org/10.5281/zenodo.4564399

>>>>

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.\footnote{The exact command can be found : \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

\begin{figure}
	\centering
		\begin{multicols}{1}
			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
		\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

{\color{red} N.B. Manual decision, not the automatic strike system}
\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }
\begin{figure*}
\centering
	\begin{multicols}{2}
		\includegraphics[scale=0.2]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
		\includegraphics[scale=0.2]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	\end{multicols}
	\begin{multicols}{2}
		\includegraphics[scale=0.2]{./img/globalresearch/tweet.png} 
		\includegraphics[scale=0.2]{./img/globalresearch/warning.png}
	\end{multicols}
%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
\caption{}
\label{fig4}
\end{figure*}

@@

\begin{figure}
\centering
\begin{multicols}{1}
\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30_2.png}
    \end{multicols}
\begin{multicols}{1} 
\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30.png}
\end{multicols}
\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
\label{fig8}
\end{figure}

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID19 or presidential elections) and  redirect users to a URL link to get more context. Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts. At the account level, notices can indicate whether an account has been temporarily or permanently suspended. 
\smallskip

In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets. More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''. Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that only $3$ tweets got labelled after being reported by a user.

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''. In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources. Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''. We find 32 other tweets, among our set of collected tweets, who share the exact same URL link in our the previous example and among those 32 only 5 tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of the interstitials placement.

Finally, to the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01_2.png}
	\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
	\end{multicols}
	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
	\label{fig9}
\end{figure}

Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} The information panel contains main information about the topic from independent third party partners. Youtube states that these panels exist regardless of the video point of view. In addition , these panels are not available in all languages and countries yet. (“Information panel giving topical context”)

Based on a video list (171 videos) checked by fact checkers and marked to have misinformation. We collected the information panels in each video by scrapping the content of the web and connecting to a US server. Four types of information panels were found in the list of visited videos. The first information panel gives info about COVID19 as in Fig \ref{fig9}, the second is about Vaccine as in Fig \ref{fig9} , the third is about Climate change as in Fig \ref{fig9} and last information panel showed on a COVID19 video about the US voting as in Fig \ref{fig9}.

We classified the list of videos examined for the information panel based on its content as in Table \ref{tab2}. The Table shows the number of videos with a panel in each category. For COVID and vaccine related videos more than half of the videos had a panel, nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same. In addition, we noticed for COVID when the video title doesn’t include keywords like (Testing, Pandemic, COVID, coronavirus) , the video wouldn’t have a panel associated with it, and in some cases when the video title have variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either. Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
For climate change we only examined 18 misleading videos and we found 72\% of them didn’t have a panel. Lastly , for the general health category, we included the videos that weren’t related to COVID but had misinformation in topics like fake cures for cancer, abortion,  and viruses; there was no information panel in all these videos. Therefore, we suspect that youtube just add information panels to  the most controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.

\begin{table}[] 
\begin{tabular}{|c|c|c|c|c|}
\hline
Category       & \begin{tabular}[c]{@{}c@{}}With information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without Information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP\\ percentage\end{tabular} \\ \hline
General Health & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
COVID          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
Climate change & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
\end{tabular}
\caption{}
\label{tab2}
\end{table}

@@

{ \color{pink} 
\begin{itemize}

	\item For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria. We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore. This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.

	\item To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent. But too much transparency on how the regulation policies are exactly implemented can actually backfire. For example YouTube is certainly applying an 'information' banner on all videos mentioning Covid and related terms in their title. Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'. If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation. There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.

	\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms. For example Newsguard, blablabla... In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2

	\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.

	\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+

	\item Make point about the communication of platforms for their policy: 4R of Youtube, RRI of Facebook,

	\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior.

\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}

	\item After a channel gets suspended or a video is deleted the data related to them is removed from the youtube API. This is a problem that affected the study to investigate the suspension reasons or the removal. For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from youtube because they contain content that is against the youtube guidelines and their data got removed from the API.

	\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... 
	\item business model

\end{itemize}}
\newpage

@@
